TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-11 paper/paper.tex
Minor correction on Methods

	\subsection{Selecting TCP congestion algorithms}	
	In order to select the most common TCP congestion algorithms desk research will be performed. Results of scientific reports will show which algorithms are used more often than other algoritms. Based on those results a list of TCP congestion algorithms will be composed.

@@

		\subsubsection{Algorithm Characteristics}
		The BBR algorithm depends on the parameters BBR.BtlBw and BBR.RTprop. Those parameters are estimates defined by the BBR algorithm. \\texttt{BtlBw} contains the bandwidth available to data transmissions ...
		- Includes characteristics of the algorithms. To what do the TCP congestion algorithms respond according to literature? And how do they deal with that (If available in literature).

>>>>

	\subsection{Selecting TCP congestion algorithms}	
	In order to select the most common TCP congestion algorithms desk research will be performed. This desk research will show which algorithms are used more often than other algoritms by looking for the default algorithms in Operating Systems. Based on those results a list of TCP congestion algorithms will be composed.

@@

		\subsubsection{Algorithm Characteristics}
		The BBR algorithm depends on the parameters BBR.BtlBw and BBR.RTprop. Those parameters are estimates defined by the BBR algorithm. \texttt{BtlBw} contains the bandwidth available to data transmissions ...
\\
\\

		- Includes characteristics of the algorithms. To what do the TCP congestion algorithms respond according to literature? And how do they deal with that (If available in literature).
